\begin{problem}{Easy Compare-and-Set}{standard input}{standard output}{2 seconds}{512 megabytes}

Let us define ``Compare-and-Set'' operation for a global variable $v$. The operation checks if the variable is equal to $a$. If that's true, the variable value changes to $b$ and the operation succeeds. Otherwise, the variable doesn't change and the operation fails. Let us denote the operation as $\operatorname{CAS}(a,b)$.

Imagine that you are given a list of such operations $\operatorname{CAS}(a_1,b_1), \dots, \operatorname{CAS}(a_n,b_n)$. Also, you are given an initial value for the variable, $c$, and a list of wishes $w_1, \dots w_n$, where $w_i$ tells whether the operation $\operatorname{CAS}(a_i,b_i)$ should be successful. Your task is to determine the order of operations execution so that all the wishes are satisfied.

\InputFile
The first line contains two integers $n$ and $c$ ($1 \le n \le 10^5$; $1 \le c \le 10^9$)~--- the number of operations and the initial value of the variable.

Each of the next $n$ lines contains three integers $a_i, b_i, w_i$ ($1 \le a_i, b_i \le 10^9$; $0 \le w_i \le 1$), denoting $\operatorname{CAS}(a_i, b_i)$ operation that you wish to be successful if $w_i = 1$ and unsuccessful if $w_i = 0$. The operations are numbered from $1$ to $n$ in order of input.

\OutputFile
If no correct order of operations exists, output a single word ``\t{No}''.

Otherwise, output a word ``\t{Yes}'' followed by $n$ distinct integers $p_1, p_2, \ldots p_n$ ($1 \le p_i \le n$), meaning that operation $p_1$ should be executed first, then operation $p_2$, and so on. 
If there are several possible orders, output any of them.


\Examples

\begin{example}
\exmpfile{example.01}{example.01.a}%
\exmpfile{example.02}{example.02.a}%
\end{example}

\end{problem}

